\section{Abstract}

This project generally consists of two tasks. The first task was to implement a tournament like setup in which the implemented players play the iterated prisoners dilemma. As a matter of fact, this is nothing new (see \cite{axelrod}) and has been studied extensive. So this leads us to the second part of this project. The standard tournament, as it was played by Axelrod is augmented by noise, whereas the difference between two kind of noises were made. One kind changes cooperation into defection, which forces the overall reward down and prefers defective players, because cooperative ones are exploited more. The other kind of noise changes defection into cooperation, which actually has has a different impact on the system. If defections are hidden behind cooperations, the average reward increases because the cooperative players stay cooperation and do not notice the exploitation.\\

The augmentation of noise makes the tournament much more realistic, because between humans there is always some miscommunication. This project illustrates, that miscommunication whereas cooperation corrupted by defection decreases the reward of the whole system and not just the tricked ones. Further the simulations indicates, that complete information is not the best, contrary to intuition. Defections which are seen as cooperations help every participant, but most of all the friendly ones.\\

Furthermore some learning and evolving strategies have been implemented. One of this learning strategies can adapt best of all strategies to the noise, by just changing to another strategy, if the reward of this one is bigger. The evolutionary strategy was not really capable to adapt to the noise, because it is relying one taken decisions of past rounds and noise corrupts it's data.    